---
title: "HLM stuff"
output: html_document
---
This needs the new data set included
```{r message=FALSE, warning=FALSE}
#load("~/Desktop/hmiout40")
#load("~/Documents/LA Postdoc stuff copy/RData/LASSO/Denver-Chico_collaboration/Physics_Equity_new/hmifall2018_m10_better")

#Ben data
#load("~/Box Sync/work/Research/R stuff/hmifall2018_m10_better")

load("~/Documents/LASSO Data/hmi_data_1_10_19_xochith")

library(mitools)
library(stargazer)
library(lme4)
library(nlme)
library(mice)
library(mitml)
library(multcomp)
library(foreach)
library(ggplot2)
library(stringr)
library(kableExtra)
library(dplyr)  #I load dplyr last because some of its functions (select) will be masked by plyr and it is a PITA to debug

plot_col <- c('#66c2a5', '#fc8d62', '#8da0cb')
cbbpalette <- c('#000000','#E69F00','#56B4E9')

```

Creating mitml and extra variables
```{r}
MIdata<-mids2mitml.list(hmi_1_19_xochith) #converts file type

thing <- list()
for (i in 1:10){
  temp <- MIdata[[i]]
  class_means <- temp %>% group_by(course_id) %>% summarise(pre_mean_class = mean(pre_score))
  class_means$class_pre_cent <- class_means$pre_mean_class - mean(class_means$pre_mean_class)
  temp <- left_join(temp,class_means, by="course_id")
  temp$stud_pre_cent <- temp$pre_score - temp$pre_mean_class
  temp$gain <- temp$post_score - temp$pre_score
  temp$colab_no_la <- as.numeric(temp$colab_no_la)
  temp$la_in_lab <- as.numeric(temp$la_in_lab)
  temp$la_in_lecture <- as.numeric(temp$la_in_lecture)
  temp$la_in_rec <- as.numeric(temp$la_in_rec)
  temp$first_time <- as.numeric(temp$first_time)
  temp$coll <- temp$colab_no_la + temp$la_in_lab + temp$la_in_lecture + temp$la_in_rec - 4
  temp$colab_no_la <- as.factor(temp$colab_no_la)
  temp$la_in_lab <- as.factor(temp$la_in_lab)
  temp$la_in_lecture <- as.factor(temp$la_in_lecture)
  temp$la_in_rec <- as.factor(temp$la_in_rec)
  temp$first_time <- as.factor(temp$first_time)
  temp$coll <- as.factor(temp$coll)
  temp$retake <- as.factor(ifelse(temp$first_time==1,1,0))
  temp$lec <- as.factor(ifelse(temp$coll==1,0,1))
  temp$course_id <- as.factor(temp$course_id)
  #assign(df.names[i], temp)
  thing[[i]] <- temp
  }
MIdata <- as.mitml.list(thing)                        
```


Models
```{r}
#We need these models for making the graphs. We can't just call them into the lmer because it doesn't work
model_1 <- gain~1 + (1|course_id)
model_2 <- gain~1 + class_pre_cent + (1|course_id)
model_3 <- gain~1 + stud_pre_cent + (1|course_id)
model_3.1 <- gain~1 + retake + (1|course_id)
model_3.2 <- gain~1 + stud_pre_cent + retake + (1|course_id)
# we want to compare model 4 and model 5 to see if we should separate these two
model_4 <- gain~1 + stud_pre_cent + coll + (1|course_id)
model_5 <- gain~1 + stud_pre_cent + colab_no_la + used_las + (1|course_id)

#We want to see if breaking up used_la helps the fit of the model.
model_6 <- gain~1 + stud_pre_cent  + colab_no_la + la_in_lab + la_in_lecture + la_in_rec + (1|course_id)

#We want to test if letting student_pre_cent vary improves the fit of the model.
model_7 <- gain~1 + stud_pre_cent  + colab_no_la + la_in_lab + la_in_lecture + la_in_rec + (1 + stud_pre_cent|course_id)
model_8 <- gain~1 + stud_pre_cent  + colab_no_la + used_las + (1 + stud_pre_cent|course_id)

mod_1<-with(MIdata,{lmer(gain~1 + (1|course_id))})
mod_2<-with(MIdata,{lmer(gain~1 + class_pre_cent + (1|course_id))})
mod_2.1<-with(MIdata,{lmer(gain~1 + ACTCAT + (1|course_id))})

mod_3<-with(MIdata,{lmer(gain~1 + stud_pre_cent + (1|course_id))})
mod_3.1<-with(MIdata,{lmer(gain~1 + retake + (1|course_id))})
mod_3.2<-with(MIdata,{lmer(gain~1 + stud_pre_cent + retake + (1|course_id))})
mod_4<-with(MIdata,{lmer(gain~1 + stud_pre_cent + coll + (1|course_id))})
mod_5<-with(MIdata,{lmer(gain~1 + stud_pre_cent + colab_no_la + used_las + (1|course_id))})
mod_5.1<-with(MIdata,{lmer(gain~1 + stud_pre_cent + colab_no_la + used_las + retake + (1|course_id))})
mod_6<-with(MIdata,{lmer(gain~1 + stud_pre_cent  + colab_no_la + la_in_lab + la_in_lecture + la_in_rec + retake +  (1|course_id))})
mod_6.1<-with(MIdata,{lmer(gain~1 + stud_pre_cent  + colab_no_la + la_in_lab + la_in_lecture + la_in_rec + retake +  class_pre_cent + (1|course_id))})


mod_7<-with(MIdata,{lmer(gain~1 + stud_pre_cent  + colab_no_la + la_in_lab + la_in_lecture + la_in_rec + retake + ACTCAT + ( 1|course_id))})
mod_7.1<-with(MIdata,{lmer(gain~1 + stud_pre_cent  + colab_no_la + la_in_lab + la_in_lecture + la_in_rec + retake + ACTCAT + (1|course_id)+ (1|institution_id))})
mod_7.2<-with(MIdata,{lmer(gain~1 + stud_pre_cent  + ACTCAT*colab_no_la + ACTCAT*la_in_lab + ACTCAT*la_in_lecture + ACTCAT*la_in_rec + retake + (1|course_id) + (1|institution_id))})
mod_8<-with(MIdata,{lmer(gain~1 + stud_pre_cent  + colab_no_la + used_las + (1 + stud_pre_cent|course_id))})
#full model




```
#average student posttest score is 54.59

```{r}
testEstimates(mod_1, var.comp=TRUE)
testEstimates(mod_2, var.comp=TRUE)
testEstimates(mod_2.1, var.comp=TRUE)

testEstimates(mod_3, var.comp=TRUE)
testEstimates(mod_3.1, var.comp=TRUE)
testEstimates(mod_3.2, var.comp=TRUE)

testEstimates(mod_4, var.comp=TRUE)
testEstimates(mod_5, var.comp=TRUE)
testEstimates(mod_5.1, var.comp=TRUE)
testEstimates(mod_6, var.comp=TRUE) #best model
testEstimates(mod_6.1, var.comp=TRUE)
testEstimates(mod_7, var.comp=TRUE)
testEstimates(mod_7.1, var.comp=TRUE)
testEstimates(mod_7.2, var.comp=TRUE)
#testEstimates(mod_8, var.comp=TRUE)



```

```{r}
mod_13.0<-with(MIdata,{lmer(gain~1 + (1|course_id) + (1|institution_id))})
mod_13.1<-with(MIdata,{lmer(gain~1 + stud_pre_cent  +(1|course_id) + (1|institution_id))})
mod_13.2<-with(MIdata,{lmer(gain~1 + retake + (1|course_id) + (1|institution_id))})
mod_13.3<-with(MIdata,{lmer(gain~1 + stud_pre_cent  +  retake + (1|course_id) + (1|institution_id))})
#The ACTCAT isn't super useful
#mod_13.4<-with(MIdata,{lmer(gain~1 + ACTCAT + (1|course_id) + (1|institution_id))}) 
#mod_13.41<-with(MIdata,{lmer(gain~1 + stud_pre_cent  +  retake + ACTCAT + (1|course_id) + (1|institution_id))})
mod_13.5<-with(MIdata,{lmer(gain~1 + stud_pre_cent  +  retake + colab_no_la +used_las + (1|course_id) + (1|institution_id))})
mod_13.6<-with(MIdata,{lmer(gain~1 + stud_pre_cent  +  retake + colab_no_la + la_in_lab + la_in_lecture + la_in_rec + (1|course_id) + (1|institution_id))})

```
 Thoughts from three level analysis. Centered pretest score drops student level variance ~30 total and 10% at level. Retake drops institutional level variance 3 total and ~15% at that level. ACTCAT increases institutional level variance 3 toatal and ~15% Also small and not statistically significant.
 
Doing a 2-level model instead of a 3 level model just moves the institutional variance into the course level variance.
```{r}
testEstimates(mod_13.0, var.comp=TRUE)
testEstimates(mod_13.1, var.comp=TRUE)
testEstimates(mod_13.2, var.comp=TRUE)
testEstimates(mod_13.3, var.comp=TRUE)
#testEstimates(mod_13.4, var.comp=TRUE)
#testEstimates(mod_13.41, var.comp=TRUE)
testEstimates(mod_13.5, var.comp=TRUE)
testEstimates(mod_13.6, var.comp=TRUE)
testEstimates(mod_6, var.comp=TRUE)
```


This makes a table for the model development. Two sections need to be modified. The models and the equation column.
```{r}
models <- c("mod_1","mod_2","mod_3","mod_4","mod_5","mod_6","mod_7")

mod_var_tab <- data_frame(model = NA,
                          level2 = NA,
                          level1 = NA,
                          ICC = NA)

for(i in 1:7){
  temp <- testEstimates(get(models[i]), var.comp=TRUE)
  mod_var_tab[i,1] <- models[i]
  mod_var_tab[i,2] <- temp$var.comp[1]
  mod_var_tab[i,3] <- temp$var.comp[2]
  mod_var_tab[i,4] <- temp$var.comp[3]
  }

mod_var_tab$lvl1change <- (mod_var_tab$level1[1]- mod_var_tab$level1)/mod_var_tab$level1[1]
mod_var_tab$lvl2change <- (mod_var_tab$level2[1]- mod_var_tab$level2)/mod_var_tab$level2[1]

mod_var_tab$equation <- c(model_1, model_2, model_3, model_4, model_5, model_6, model_7)
```


```{r}
pool_and_cov_diffwm <- function(x,y){
  get.est <- foreach(i=1:10, .combine=rbind) %do% {
  sxp3 <- summary(glht(x[[i]], linfct=y)) #specifically for post3
  covp3 <- vcov(glht(x[[i]], linfct=y))
  data.frame(imp=i, 
             group=rownames(sxp3$linfct),
             d = sxp3$test$coefficients, 
             var.d = (sxp3$test$sigma)^2,
             cov = covp3)
}


p3est <- get.est %>% group_by(group) %>% 
                  summarise(Q = mean(d), 
                            U = mean(var.d), 
                            B = var(d), 
                            T = U + ((1+1/max(imp))*B), 
                            LCL = Q - 1.96*sqrt(T), 
                            UCL = Q + 1.96*sqrt(T),
                            SE = sqrt(T)) 

return <- p3est}
```

```{r}

TL = c(1,0,0,0)
CL = c(1,0,1,0)
LA = c(1,0,0,1)

contrast_forms_mod5 <- rbind('Traditional Lecture'=TL, 
                             'Collaborative No LA'=CL,
                             'LA Supported'=LA)

contrast_g5_est <- pool_and_cov_diffwm(mod_5,contrast_forms_mod5)

contrast_g5_est$group <- factor(contrast_g5_est$group, levels = c("Traditional Lecture", "Collaborative No LA", "LA Supported"))

ggplot(data=contrast_g5_est, aes(x=group, y=Q, fill=group )) +
  geom_bar(stat = "identity") + 
  geom_errorbar(aes( ymax= Q+1*SE, ymin=Q-1*SE, width=0.5))+
  theme(legend.position = "none", 
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), 
        axis.line = element_line(colour = "black"), text = element_text( color = "black"), axis.title.x = element_blank()) + #size=16,
  ylab("Gain (Percentage Points)") +
  scale_fill_manual(name="Instruction",
                     breaks= c("Traditional Lecture", "Collaborative No LA", "LA Supported"),
                     labels=c("Traditional Lecture", "Collaborative No LA", "LA Supported"),
                     values=plot_col) 

kable(contrast_g5_est[c(1,2,6,7)], digits = 2)
```

```{r}
TL = c(1,0,0,0,0,0)
CL = c(1,0,1,0,0,0)
LALec = c(1,0,0,0,1,0)
LARec = c(1,0,0,0,0,1)
LALab = c(1,0,0,1,0,0)


contrast_forms_mod6 <- rbind('Traditional Lecture'=TL, 'Collaborative No LA'=CL, 
                          'LA in Lecture'=LALec, 'LA in Recitation'=LARec, 
                          'LA in Lab'=LALab)

contrast_g6_est <- pool_and_cov_diffwm(mod_6,contrast_forms_mod6)

contrast_g6_est$group <- factor(contrast_g6_est$group, levels = c("Traditional Lecture", "Collaborative No LA", "LA in Lecture", "LA in Recitation", "LA in Lab"))
contrast_g6_est$filler <- c("2","3","3","3","1")

ggplot(data=contrast_g6_est, aes(x=group, y=Q, fill=filler )) +
  geom_bar(stat = "identity") + 
  geom_errorbar(aes( ymax= Q+1*SE, ymin=Q-1*SE, width=0.5))+
  theme(legend.position = "none", 
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), 
        axis.line = element_line(colour = "black"), text = element_text( color = "black"), axis.title.x = element_blank()) + #size=16,
  ylab("Gain (Percentage Points)") +
  scale_fill_manual(name="Instruction",
                     breaks= c(2,3,3,3,1),
                     labels=c("Collaborative No LA" , "LA in Lab", "LA in Lecture", "LA in Recitation",  "Traditional Lecture"),
                     values=plot_col) 

kable(contrast_g6_est[c(1,2,6,7)], digits = 2)
```


#Calculating the descriptive statistics 
##building tables

```{r}
student_means <- foreach(i=1:10, .combine=rbind) %do% {
  temp <- MIdata[[i]]
  temp$instruction <- ifelse(temp$used_las==1,"Used LAs",ifelse(temp$colab_no_la==1,"Collaborative No LA","Lecture"))
  student_means <- temp %>% group_by(instruction) %>% summarise(mean_gain = mean(gain))
  return <- student_means
  }

student_means_la_use <- foreach(i=1:10, .combine=rbind) %do% {
  temp <- MIdata[[1]]
  temp <- temp[temp$used_las==1,]
  temp$instruction <- ifelse(temp$la_in_lecture ==1,"LA in Lecture",ifelse(temp$la_in_lab ==1,"LA in Lab","LA in Recitation"))
  student_means_1 <- temp %>% group_by(instruction) %>% summarise(gain = mean(gain))
  return <- student_means_1
}

student_means_tab <- data.frame(Level = "Student",
                            Used_LAs = mean(student_means$mean_gain[student_means$instruction=="Used LAs"]), 
                            Collab_No_LA = mean(student_means$mean_gain[student_means$instruction=="Collaborative No LA"]),
                            Lecture = mean(student_means$mean_gain[student_means$instruction=="Lecture"]), 
                            All = mean(student_means$mean_gain),
                              la_in_lecture = mean(student_means_la_use$gain[student_means_la_use$instruction=="LA in Lecture"]),
                              la_in_recitation = mean(student_means_la_use$gain[student_means_la_use$instruction=="LA in Recitation"]),
                              la_in_lab = mean(student_means_la_use$gain[student_means_la_use$instruction=="LA in Lab"]))


class_means <- foreach(i=1:10, .combine=rbind) %do% {
  temp <- MIdata[[i]]
  temp$instruction <- ifelse(temp$used_las==1,"Used LAs",ifelse(temp$colab_no_la==1,"Collaborative No LA","Lecture"))
  class_means <- temp %>% group_by(course_id) %>% summarise(gain = mean(gain))
  class_means <- left_join(class_means,unique(temp[c(2,23)]), by = "course_id")
  class_means <- class_means_1 %>% group_by(instruction) %>% summarise(gain = mean(gain))
  return <- class_means
}

class_means_la_use <- foreach(i=1:10, .combine=rbind) %do% {
  temp <- MIdata[[i]]
  temp <- temp[temp$used_las==1,]
  temp$instruction <- ifelse(temp$la_in_lecture ==1,"LA in Lecture",ifelse(temp$la_in_lab ==1,"LA in Lab","LA in Recitation"))
  class_means <- temp %>% group_by(course_id) %>% summarise(gain = mean(gain))
  class_means <- left_join(class_means,unique(temp[c(2,23)]), by = "course_id")
  class_means <- class_means %>% group_by(instruction) %>% summarise(gain = mean(gain))
  return <- class_means
}
 
class_means_1 <- foreach(i=1:10, .combine=rbind) %do% {
  temp <- MIdata[[i]]
  temp$instruction <- ifelse(temp$used_las==1,"Used LAs",ifelse(temp$colab_no_la==1,"Collaborative No LA","Lecture"))
  class_means_1 <- temp %>% group_by(course_id) %>% summarise(gain = mean(gain))
  class_means_1 <- left_join(class_means_1,unique(temp[c(2,23)]), by = "course_id")
  return <- class_means_1
}


class_means_tab <- data_frame(Level = "Course",
                              Used_LAs = mean(class_means_1$gain[class_means_1$instruction=="Used LAs"]),
                              Collab_No_LA = mean(class_means_1$gain[class_means_1$instruction=="Collaborative No LA"]),
                              Lecture = mean(class_means_1$gain[class_means_1$instruction=="Lecture"]),
                              All = mean(class_means_1$gain),
                              la_in_lecture = mean(class_means_la_use$gain[class_means_la_use$instruction=="LA in Lecture"]),
                              la_in_recitation = mean(class_means_la_use$gain[class_means_la_use$instruction=="LA in Recitation"]),
                              la_in_lab = mean(class_means_la_use$gain[class_means_la_use$instruction=="LA in Lab"]))


temp <- MIdata[[1]]
class_length_tab <- data_frame(Level = "Course",
                              Used_LAs = length(unique(temp$course_id[temp$used_las==1])),
                              Collab_No_LA = length(unique(temp$course_id[temp$colab_no_la ==1])),
                              Lecture = length(unique(temp$course_id[temp$lecture==1])),
                              All = length(unique(temp$course_id)),
                              la_in_lecture = length(unique(temp$course_id[temp$la_in_lecture==1])),
                              la_in_recitation = length(unique(temp$course_id[temp$la_in_rec==1])),
                              la_in_lab = length(unique(temp$course_id[temp$la_in_lab==1])))

student_length_tab <- data_frame(Level = "Student",
                              Used_LAs = length((temp$student_id[temp$used_las==1])),
                              Collab_No_LA = length((temp$student_id[temp$colab_no_la ==1])),
                              Lecture = length((temp$student_id[temp$lecture==1])),
                              All = length((temp$student_id)),
                              la_in_lecture = length((temp$student_id[temp$la_in_lecture==1])),
                              la_in_recitation = length((temp$student_id[temp$la_in_rec==1])),
                              la_in_lab = length((temp$student_id[temp$la_in_lab==1])))



descriptive_table <- bind_rows(student_length_tab,class_length_tab,student_means_tab,class_means_tab)
kable(descriptive_table, digits=1)
```

```{r}
class_means <- foreach(i=1:10, .combine=rbind) %do% {
  temp <- MIdata[[i]]
  class_means <- temp %>% group_by(course_id) %>% summarise(gain = mean(gain))
   return <- class_means
}

class_means <- class_means %>% group_by(course_id) %>% summarise(gain = mean(gain))

temp$instruction <- ifelse(temp$used_las==1,"Used LAs",ifelse(temp$colab_no_la==1,"Collaborative No LA","Lecture"))
temp$instruction_la_use <- ifelse(temp$lecture==1,"Lecture",
                                    ifelse(temp$colab_no_la==1,
                                           "Collaborative No LA",
                                           ifelse(temp$la_in_lab==1,"LA in Lab",
                                                  ifelse(temp$la_in_lecture==1,"LA in Lecture","LA in Recitation"))))
class_size <- temp %>% group_by(course_id) %>% summarise(N = length(student_id))

class_means <- left_join(class_means,unique(temp[c(2,23,24)]), by = "course_id")
class_means <- left_join(class_means,class_size, by = "course_id")
```

```{r}
ggplot(class_means, aes(x=gain, y= N, color=instruction)) +geom_point()

library(cowplot)

sp <- ggplot(data=class_means, aes(x=gain,y=N,col=instruction)) +geom_point(alpha=0.5, size=1) +
  xlim(0,50)+
  ylim(0,650)

xplot <-  ggplot(data=class_means, aes(x=gain, fill=instruction,color=instruction) ) + geom_density(alpha=0.3)+ 
  theme(legend.position = 'none', 
        axis.line=element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks=element_blank(), 
        axis.title.x=element_blank(),
        axis.title.y=element_blank())+
  xlim(0,50)
  
  
yplot <-  ggplot(data=class_means, aes(x=N, fill=instruction,color=instruction) ) +geom_density(alpha=0.3)+ 
  theme(legend.position = 'none', 
        axis.line=element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks=element_blank(), 
        axis.title.x=element_blank(),
        axis.title.y=element_blank())+
  xlim(0,650) +
  coord_flip()

plot_grid(xplot, NULL, sp+theme(legend.position = 'none') , yplot, ncol = 2, align = "hv", 
          rel_widths = c(2, 1), rel_heights = c(1, 2))

```

```{r}
ggplot(class_means, aes(x=gain, y= N, color=instruction_la_use)) +geom_point()

library(cowplot)

sp <- ggplot(data=class_means, aes(x=gain,y=N,col=instruction_la_use)) +geom_point(alpha=0.5, size=1) +
  xlim(0,50)+
  ylim(0,650)

xplot <-  ggplot(data=class_means, aes(x=gain, fill=instruction_la_use,color=instruction_la_use) ) + geom_density(alpha=0.3)+ 
  theme(legend.position = 'none', 
        axis.line=element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks=element_blank(), 
        axis.title.x=element_blank(),
        axis.title.y=element_blank())+
  xlim(0,50)
  
  
yplot <-  ggplot(data=class_means, aes(x=N, fill=instruction_la_use,color=instruction_la_use) ) +geom_density(alpha=0.3)+ 
  theme(legend.position = 'none', 
        axis.line=element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks=element_blank(), 
        axis.title.x=element_blank(),
        axis.title.y=element_blank())+
  xlim(0,650) +
  coord_flip()

plot_grid(xplot, NULL, sp+theme(legend.position = 'none') , yplot, ncol = 2, align = "hv", 
          rel_widths = c(2, 1), rel_heights = c(1, 2))

```

```{r}
ggplot(class_means[class_means$instruction=="Used LAs",], aes(x=gain, y= N, color=instruction_la_use)) +geom_point()

library(cowplot)

sp <- ggplot(data=class_means[class_means$instruction=="Used LAs",], aes(x=gain,y=N,col=instruction_la_use)) +geom_point(alpha=0.5, size=1) +
  xlim(0,50)+
  ylim(0,650)

xplot <-  ggplot(data=class_means[class_means$instruction=="Used LAs",], aes(x=gain, fill=instruction_la_use,color=instruction_la_use) ) + geom_histogram(alpha=0.3, position = "dodge")+ 
  theme(legend.position = 'none', 
        axis.line=element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks=element_blank(), 
        axis.title.x=element_blank(),
        axis.title.y=element_blank())+
  xlim(0,50)
  
  
yplot <-  ggplot(data=class_means[class_means$instruction=="Used LAs",], aes(x=N, fill=instruction_la_use,color=instruction_la_use) ) +geom_histogram(alpha=0.3, position = "dodge")+ 
  theme(legend.position = 'none', 
        axis.line=element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks=element_blank(), 
        axis.title.x=element_blank(),
        axis.title.y=element_blank())+
  xlim(0,650) +
  coord_flip()

plot_grid(xplot, NULL, sp+theme(legend.position = 'none') , yplot, ncol = 2, align = "hv", 
          rel_widths = c(2, 1), rel_heights = c(1, 2))

```


#Assumption checking

```{r}
	for (i in 1:10) {
  D1 <- lmer(model_6,data=MIdata[[i]])
  print(plot(D1, xlab="Fitted Value", ylab="Residual Variance"))
}
 

for (i in 1:10) {
  D1 <- lmer(model_6,data=MIdata[[i]])
#visual homogeneity of variance
MIdata[[i]]$Model.F.Res <- residuals(D1) #extracts the residuals and places them in a new column in our original data table
MIdata[[i]]$Abs.Model.F.Res <-abs(MIdata[[1]]$Model.F.Res) #creates a new column with the absolute value of the residuals
print(boxplot(MIdata[[i]]$Model.F.Res ~ MIdata[[i]]$course_id, xlab = "Course", ylab = "Residuals" ))
}

for (i in 1:10) {
  D1 <- lmer(model_6,data=MIdata[[i]])
#Assumption of Normality or residuals: want points to be near the line
print(qqmath(D1))
}
```
 # This produces a table of the pvalues for the correlations between the student level variables for pretest and the residuals. These p values should be large to indicate that there isn't a correlation
```{r}
res_corr <- data_frame(it =NA,
                       with_pre_score = NA,
                       with_cent_pre = NA)
 for (i in 1:10) {
res_corr[i,1] <- i
D1 <- lmer(model_6,data=MIdata[[i]])
temp <- cor.test(resid(D1), MIdata[[i]]$pre_score)
res_corr[i,2] <-  temp$p.value 
temp <-  cor.test(resid(D1), MIdata[[i]]$stud_pre_cent)
res_corr[i,3] <- temp$p.value
 }

kable(res_corr)
```	

```{r}
lev_p <- data_frame(it =NA,
                       p_values = NA)
 for (i in 1:10) {
lev_p[i,1] <-i
D1 <- lmer(model_6,data=MIdata[[i]])
MIdata[[i]]$Model.F.Res<- residuals(D1) #extracts the residuals and places them in a new column in our original data table
MIdata[[i]]$Abs.Model.F.Res <-abs(MIdata[[i]]$Model.F.Res) #creates a new column with the absolute value of the residuals
Levene.Model.F <- lm(Model.F.Res ~ course_id, data=MIdata[[i]]) #ANOVA of the residuals
temp <-anova(Levene.Model.F) #displays the results: want a p>0.05
lev_p[i,2] <- temp$`Pr(>F)`[[1]]
 }

kable(lev_p)
```

